### 2010-04-01 docs/architecture/architecture.tex
more reorganization
lots of additions

 boxlib is a library for describing meshes consisting of a union
 of boxes.  The boxlib modules define the basic datatypes used
 in MAESTRO.

@@

 Simple Fortran-based analysis routines (e.g.\ extract a line from a
 multidimensional dataset) that operate on boxlib plotfiles.

@@

@@

   Several sub-directories containing routines to generate
   1D initial conditions in hydrostatic equilibrium for 
   mapping onto the MAESTRO grid.

@@

   Any file that you place in a sub-directory here takes 
   precedence over a file of the same name in {\tt MAESTRO/}.
   This allows problems to have custom versions of the main
   MAESTRO routines (e.g.\ initial conditions via {\tt initdata.f90}.

@@

In this section we describe some of the standard problems that come
with MAESTRO, how to run the code, and how to look at the output.

@@

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.

@@

Spherical heat maps a spherical star (a Chandrasekhar-mass white
dwarf) onto the Cartesian domain and uses an external heat source to
cause the star to expand.  This is the 3-d analogue of the {\tt
  test\_basestate} unit test.  This problem was discussed in
\cite{multilevel}.

@@

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d}
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoint files.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoint files are named {\tt chk}{\em
  nnnnn}.

To restart a calculation from a checkpoint file, either edit the inputs
file, setting
\begin{verbatim}
  restart = n
\end{verbatim}
where {\tt n} is the step number of the checkpoint file to restart
from.  Equivalently, you can override the value in the inputs file
by adding {\tt --restart n} to the commandline, as 
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d --restart n
\end{verbatim}

\subsection{Common Runtime Parameters}

@@

Visualization and analysis are done with on the plotfiles.  The
frequency of plotfile outputting can be changed using the runtime
parameters {\tt plot\_int}, which specifies the number of steps
between output, and {\tt plot\_deltat} which specifies the simulation
time between output.  Setting {\tt plot\_int} to {\tt -1} disables
step-based outputting; setting {\tt plot\_deltat} to {\tt 0.0}
disables time-based outputting.

\subsubsection{Amrvis}

@@

Several useful analysis scripts can be found in {\tt
fParallel/data\_processing}.  The makefile there needs
to be edited to indicate which of the tools to build.

\item {\tt fextract3d}

  Extracts a 1-d slice from a plotfile, through the center of the
  domain in any coordinate direction.  Either all of the variables or
  a single variable is output.

\item {\tt fextrema}

  Outputs the min/max of each of the quantities in the plotfile.

\item {\tt ftime}

  Outputs the simulation time for one or more plotfiles.

@@

@@

@@

The minimum requirement to
define a new problem would be a {\tt GNUmakefile} which describes how
to build the application and an input file which lists the runtime
parameters.  The problem-specific executable is built in the problem
directory by typing {\tt make}.  Source files are found automatically
by searching the directories listed in the {\tt GNUmakefile}.

@@

Runtime parameters listed in the {\tt MAESTRO/\_parameters} file are
parsed at compile time and the file {\tt probin.f90} is written and
compiled.  This is a Fortran module that holds the values of the
runtime parameters and makes them available to any routine.  The
variable {\tt PROBIN\_PARAMETERS} should list all of the files that
contain runtime parameters for the current problem.  You must always
include the main {\tt ../\_parameters} file (i.e.\ {\tt
  MAESTRO/\_parameters}).  Sometimes a problem defines their own
runtime parameters, in which case, its parameter file should also
appear in {\tt PROBIN\_PARAMETERS}.
\begin{verbatim}
  PROBIN_PARAMETERS := ../_parameters
\end{verbatim}

@@

The runtime parameters for the core MAESTRO algorithm are listed
in {\tt MAESTRO/\_parameters}.  That file is parsed at compile-time
by the {\tt MAESTRO/write\_probin.py} script
(along with any other parameter files listed in the {\tt PROBIN\_PARAMETERS}
variable in the {GNUmakefile}, see \S \ref{sec:makefile}).  The script
outputs the {\tt probin.f90} source file.  Each line
in the {\tt \_parameters} file has the form:

{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value}

\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and a used to produce documentation about the
available runtime parameters.

@@

@@

@@

The routines in {\tt MAESTRO/initial\_model/} take a 1-d initial
model and map it onto a uniform grid, at the desired resolution, using
the equation of state in MAESTRO, and using MAESTRO's discretization of
hydrostatic equilibrium.

@@

MAESTRO's gridding is handled by the boxlib library.  The underlying
idea in boxlib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In boxlib, data that is on an edge is termed `nodal'
in that direction (see Figure~\ref{fig:dataloc}).  Data that is on the
corners is nodal in all spatial directions.  In MAESTRO, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

@@

To simplify the description of the underlying AMR grid, boxlib
provides a number of Fortran types.  We briefly summarize the major
data types below.

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.  Note that the
indexing in boxlib starts with $0$.}
\end{figure}

@@

\item {\tt hi = upb(mybox)} returns an array, {\tt hi(dm)}, with
     the box lower bounds

@@

The state of the star in MAESTRO is described by both a
multidimensional state and the 1D base state.  The full
multidimensional state is stored in \multifab s while the base state
is simply stored in Fortran arrays.

@@

\item {\tt extern/EOS/gamma\_law\_general} assumes an ideal gas with a mixed 
     composition and a constant ratio of specific heats, $\gamma$:
      \begin{equation}
      p = \rho e (\gamma - 1) = \frac{\rho k_B T}{\mu m_p} 
      \end{equation}
     where $k_B$ is Boltzmann's constant and $m_p$ is the mass of the
     proton.
     The mean molecular weight, $\mu$, is computed either assuming 
     electrically neutral atoms:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k}{A_k} \right )^{-1}
     \end{equation}
     or complete ionization:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k (Z_k + 1)}{A_k} \right )^{-1}
     \end{equation}
     The default is neutral, and presently one must change a parameter
     in the source code to switch between these limits.
\end{itemize}

@@

{\tt probin\_module} provides access to the runtime parameters.

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are listed in table~\ref{tab:variable_keys}.
\begin{table}[h!]
\centering
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density $\times$ specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & first species partial density, $(\rho X_1)$ \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}

\caption{\label{tab:variable_keys} {\tt variables} module common keys}
\end{table}

@@

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic boxlib data types. Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.

>>>>

 BoxLib is a library for describing meshes consisting of a union
 of boxes.  The BoxLib modules define the basic datatypes used
 in MAESTRO.

@@

 Simple Fortran-based analysis routines (e.g.\ extract a line from a
 multidimensional dataset) that operate on BoxLib datasets.

@@

 Important subdirectories include:
 \begin{itemize}
 \item {\tt constants/}

 A simple module to define physical constants

 \item {\tt EOS/}

 A collection of various EOSes for use with the code.  The two
 important ones for MAESTRO are {\tt helmeos/} and {\tt
 gamma\_law\_general/}.

 \item {\tt networks/}

 Various reaction networks for MAESTRO problems.  In addition to
 providing a routine to evolve the nuclear species due to reactions,
 the networks also define the species that are advected by the code.

 \item {\tt VODE/}

 An integration package for ODEs.  At the moment, this is used 
 for integrating various reaction networks.

@@

   Several sub-directories containing routines to generate
   1D initial conditions in hydrostatic equilibrium for 
   mapping onto the MAESTRO grid.  See \S~\ref{sec:initial_models}
   for details.

@@

   Any file that you place in a sub-directory here takes 
   precedence over a file of the same name in {\tt MAESTRO/}.
   This allows problems to have custom versions of the main
   MAESTRO routines (e.g.\ initial conditions via {\tt initdata.f90}.
   See \S~\ref{sec:makefile} for details on the build system.

@@

In this section we describe some of the standard problems that come
with MAESTRO, how to run the code, some basic runtime parameters, and
how to look at the output.

@@

The {\tt flame} problem models a planar laminar flame.  Initially cool
fuel and hot ash are put in pressure equilibrium.  Thermal diffusion
transfers heat to the fuel, driving a burning front.  This problem
does not use the traditional MAESTRO elliptic constraint, but
rather enforces $\nabla \cdot U = S$ (through the runtime parameter
{\tt do\_smallscale = T}) as discussed in \cite{SNe}.

@@

{\tt spherical\_heat} maps a spherical star (a Chandrasekhar-mass white
dwarf) onto the Cartesian domain and uses an external heat source to
cause the star to expand.  This is the 3-d analogue of the {\tt
  test\_basestate} unit test (see \S~\ref{sec:unit_tests}).  This
problem was discussed in \cite{multilevel}.

@@

To build the MAESTRO executable, simply type `{\tt make}' in the
problem directory.  The executable will have a name like
{\tt main.Linux.Intel.exe}, where the specific parts of 
the name depend on the compilers and OS used.  Each problem
will have one or more inputs files (for example, {\tt test2/inputs\_2d})
which override the default values for one or more runtime parameters.
The code is run simply as:
\begin{verbatim}
  main.Linux.Intel.exe inputs_2d
\end{verbatim}
As the code runs, it will output both plotfiles and checkpoints.
By default, the plotfiles will be named {\tt plt}{\em nnnnn}, where
the number {\em nnnnn} is the timestep number when the file was
outputted.  Similarly, the checkpoints are named {\tt chk}{\em
  nnnnn}.  BoxLib plotfiles and checkpoints are actually directories,
with the data stored in subdirectories grouped by refinement level.
Details of the simulation (number of processors used, output date,
output directory, runtime parameter values, ...) are stored in
the {\tt job\_info} file in each plotfile directory.

A large number of runtime parameters affect the code's behavior.  Any
runtime parameter can be set either in the inputs file, as {\tt parameter
  = value} or on the command line by adding {\tt --parameter value} after
listing the inputs file on the command line.  A full list of runtime
parameters is detailed in \S~\ref{sec:runtime_parameters}.  Below we
outline the most common runtime parameters.

\subsection{Controlling Timestepping and Output}

Parameters that set the maximum time for the simulation to run
include:
\begin{itemize}
\item {\tt stop\_time} is the maximum simulation time, in seconds,
      to evolve the system for.

\item {\tt max\_step} is the maximum number of steps to take.
\end{itemize}

\noindent Parameters affecting the size of the timestep include:
\begin{itemize}
\item {\tt cflfac} is a multiplicative factor ({\tt $\le 1$}) 
      applied to the advective CFL timestep

\item {\tt init\_shrink} is the factor ({\tt $\le 1$}) by which to reduce 
      the initial timestep from the estimated first timestep.
\end{itemize}

\noindent Parameters affecting output and restart include:
\begin{itemize}

\item {\tt restart} tells MAESTRO to restart from a checkpoint.  The
      value of this parameter should be the file number to restart from.

\item {\tt plot\_int} is the number of steps to take between
  outputting a plotfile

\item {\tt plot\_deltat} is the simulation time to evolve between
  outputting a plotfile.  Note: to output only based on simulation
  time, set {\tt plot\_int = -1}.

\item {\tt check\_int} is the number of steps to take between
  outputting a checkpoint.

\subsection{Defining the Grid and Boundary Conditions}

Parameters that determine the spatial extent of the grid, 
the types of boundaries, and the number of computational cells include:
\begin{itemize}

\item {\tt max\_levs } is the maximum number of grid levels in the AMR
  hierarchy to us.  {\tt max\_levs = 1} indicates running with only a
  single level spanning the whole domain.

\item {\tt n\_cellx }, {\tt n\_celly }, {\tt n\_cellz } the size of
  base level in terms of number of cells, in the $x$, $y$, and $z$
  coordinate directions.

\item {\tt max\_grid\_size } the maximum extend of a grid, in any
  coordinate direction, as measured in terms of number of cells.

\item {\tt prob\_lo\_x }, {\tt prob\_lo\_y }, {\tt prob\_lo\_z } is
  the physical coordinate of the lower extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

\item {\tt prob\_hi\_x }, {\tt prob\_hi\_y }, {\tt prob\_hi\_z } is
  the physical coordinate of the upper extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

\item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, 
      {\tt bcx\_hi }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary
   condition types at the lower (`{\tt lo}') and upper (`{\tt hi}')
   domain boundaries in the $x$, $y$, and $z$ coordinate directions.
   The different types are set via integer flags noted below:

   \begin{center}
   \begin{tabular}{ll}
   \hline
   BC type    & integer flag \\
   \hline
   periodic             & -1 \\
   inlet (user-defined) & 11 \\
   outlet               & 12 \\
   symmetry             & 13 \\
   slip wall            & 14 \\
   no-slip wall         & 15 \\
   \hline
   \end{tabular}
   \end{center}

   Note: for periodic boundaries, one must also set the corresponding
   {\tt pmask\_}\{{\em x,y,z}\} parameter.

\item {\tt pmask\_x }, {\tt pmask\_y }, {\tt pmask\_z } is set to 
   true ({\tt T}) to indicate that the boundary is periodic in the
   $x$, $y$, or $z$ coordinate directions.

Note that grid cells must be square, i.e. $\Delta x = \Delta y = \Delta z$
where $\Delta x$ on the base grid is computed as $({\tt prob\_hi\_x}
- {\tt prob\_lo\_x})/{\tt n\_cellx}$.

\subsection{Refinement Criteria}

@@

Visualization and analysis are done with on the plotfiles.  A
number of in-house and externally developed tools can work 
with BoxLib-formatted plotfiles.

\subsubsection{\tt Amrvis}

{\tt Amrvis} is a visualization tool developed at LBL for 2- and 3-d
datasets which can plot slices through 3-d datasets as well as
volume-renderings.  It is distributed separately from the MAESTRO
distribution.

@@

Several useful analysis scripts (written in Fortran 90) can be found
in {\tt fParallel/data\_processing}.  The {\tt GNUmakefile} there
needs to be edited to indicate which of the tools to build.  These
routines are described in \S~\ref{sec:analysis}.

@@

VisIt is a powerful, DOE-supported visualization tool for 2- and 3-d
datasets.  It can do contouring, volume rendering, streamlines, ...\
directly from BoxLib plotfiles (to open a plotfile in VisIt, point to
the {\tt Header} file inside the plotfile directory.  Details on
visit can be found at {\tt https://wci.llnl.gov/codes/visit/home.html}\,.

@@

\label{sec:unit_tests}

@@

Different MAESTRO problems are defined in subdirectories under
{\tt MAESTRO/}.  To add a problem, start by creating a new
sub-directory---this is where you will compile your problem and
store all the problem-specific files.

The minimum requirement to
define a new problem would be a {\tt GNUmakefile} which describes how
to build the application and an input file which lists the runtime
parameters.  The problem-specific executable is built in the problem
directory by typing {\tt make}.  Source files are found automatically
by searching the directories listed in the {\tt GNUmakefile}.
Customised versions of any source files placed in the problem-directory
override those with the same name found elsewhere.  Any unique
source files (and not simply a custom version of a file found
elsewhere) needs to be listed in a file call {\tt GPackage.mak}
in the problem-directory.

@@

Runtime parameters listed in the {\tt MAESTRO/\_parameters} file are
parsed at compile time and the file {\tt probin.f90} is written and
compiled.  This is a Fortran module that holds the values of the
runtime parameters and makes them available to any routine.  The
variable {\tt PROBIN\_PARAMETERS} should list all of the files that
contain runtime parameters for the current problem.  You must always
include the main {\tt ../\_parameters} file (i.e.\ {\tt
  MAESTRO/\_parameters}).  Sometimes a problem defines their own
runtime parameters (see \S~\ref{sec:def_runtime_param}), in which
case, its parameter file should also appear in {\tt
  PROBIN\_PARAMETERS}.
\begin{verbatim}
  PROBIN_PARAMETERS := ../_parameters
\end{verbatim}

@@

\label{sec:def_runtime_param}

The runtime parameters for the core MAESTRO algorithm are listed
in {\tt MAESTRO/\_parameters}.  That file is parsed at compile-time
by the {\tt MAESTRO/write\_probin.py} script
(along with any other parameter files listed in the {\tt PROBIN\_PARAMETERS}
variable in the {GNUmakefile}, see \S \ref{sec:makefile}).  The script
outputs the {\tt probin.f90} source file.  Each line
in the {\tt \_parameters} file has the form: 
\vskip 3mm
{\em parameter} \hskip 10em  {\em data-type} \hskip 10em  {\em value} 
\vskip 3mm
\noindent where {\em parameter} is the name of the runtime parameter,
{\em data-type} is one of \{{\tt character}, {\tt real}, {\tt
  integer}, {\tt logical}\}, and the {\em value} specifies the default
value for the runtime parameter.  Comments are indicated by a `{\tt
  \#}' character and a used to produce documentation about the
available runtime parameters.

@@

Problem-specify runtime parameters should be defined in the
problem-directory in a file called {\tt
  \_parameters}\{{\em.problem-name}\}.  This file should be added
to the {\tt PROBIN\_PARAMETERS} variable in the {\tt GNUmakefile}.

@@

\label{sec:initial_models}

@@

The routines in {\tt MAESTRO/initial\_model/} take a 1-d initial
model and map it onto a uniform grid, at the desired resolution, using
the equation of state in MAESTRO, and using MAESTRO's discretization of
hydrostatic equilibrium:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}

@@

MAESTRO's gridding is handled by the BoxLib library.  The underlying
idea in BoxLib is to allow for adaptive mesh refinement (AMR)---different
regions of the domain can have different spatial resolutions.  The
domain is broken into boxes.  At the coarsest (base) level of
refinement, the entire computational domain is covered, either by one
box or broken across many boxes.  Higher levels of refinement have
finer zones (typically $2\times$).  Only a portion of the domain may
be covered by the higher levels of refinement.  \MarginPar{Nesting?}
For parallel computations, the boxes are spread across processors, in
a fashion designed to put roughly equal amounts of work on each
processor (load balancing).

On a grid, the data can be stored at cell-centers, on a face/edge, or
on the corners.  In BoxLib, data that is on an edge is termed `nodal'
in that direction (see Figure~\ref{fig:dataloc}).  Data that is on the
corners is nodal in all spatial directions.  In MAESTRO, the state
data (density, enthalpy, velocity, $\ldots$) is generally
cell-centered.  Fluxes are nodal in the direction they represent.
A few quantities are nodal in all directions (e.g.\ $\phi$ used in
the final velocity projection).

@@

To simplify the description of the underlying AMR grid, BoxLib
provides a number of Fortran types.  We briefly summarize the major
data types below.

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.  Note that the
indexing in BoxLib starts with $0$.}
\end{figure}

@@

\item {\tt hi = upb(mybox)} returns an array, {\tt hi(dm)}, with
     the box upper bounds

@@

The state of the star in MAESTRO is described by both a
multidimensional state and the 1D base state.  The full
multidimensional state is stored in \multifab s while the base state
is simply stored in Fortran arrays.  Here we describe the
major MAESTRO data-structures.

@@

\item {\tt extern/EOS/gamma\_law\_general} assumes an ideal gas with a mixed 
     composition and a constant ratio of specific heats, $\gamma$:
      \begin{equation}
      p = \rho e (\gamma - 1) = \frac{\rho k_B T}{\mu m_p} 
      \end{equation}
     where $k_B$ is Boltzmann's constant and $m_p$ is the mass of the
     proton.
     The mean molecular weight, $\mu$, is computed assuming 
     electrically neutral atoms:
     \begin{equation}
     \mu = \left ( \sum_k \frac{X_k}{A_k} \right )^{-1}
     \end{equation}
     An option in the source code itself exists for treating the
     species as fully-ionized, but there is no runtime-parameter to
     make this switch.
\end{itemize}

eos module variables

eos input types

@@

{\tt probin\_module} provides access to the runtime parameters.
The runtime parameters appear simply as module variables.  To get the 
value of a parameter, one simply needs to `{\tt use probin\_module}'.
The preferred method is to add the `{\tt only}' clause to the
{\tt use} statement and explicitly list only those parameters that
are used in the routine.  Defining new runtime parameters is
described in \S~\ref{sec:def_runtime_param}.

@@

The {\tt variables} module provides integer keys to index the state
multifabs and other arrays dealing with the scalar quantities.  The
most commonly used keys are are:

\begin{center}
\begin{tabular}{ll}
\hline
{\tt rho\_comp}  & density \\
{\tt rhoh\_comp} & density $\times$ specific enthalpy, $(\rho h)$ \\
{\tt spec\_comp} & first species partial density, $(\rho X_1)$ \\
{\tt temp\_comp} & temperature \\
\hline
\end{tabular}
\end{center}

@@

\noindent Here, the {\tt bl\_types} and {\tt multifab\_module} modules
bring in the basic BoxLib data types. Specifically, here, {\tt
bl\_types} defines {\tt dp\_t} which is the {\tt kind} used for
declaring double precision data, and {\tt multifab\_module} defines
the \multifab\ data type.  The {\tt geometry} module is a MAESTRO
module that provides the dimensionality ({\tt dm}) and the number of 
levels ({\tt nlevs}).  The {\tt variables} module is a MAESTRO
module that provides integer keys for indexing the state arrays.  In
this case the integer {\tt rho\_comp} refers to the location in the
state array corresponding to density.
